2nd_draft

### 2020-03-17 src/2nd_draft.Rmd
y lab fixed

boxplot(mspe1.la, 
        mspe1.ri,
        # mspe1.el, 
        # mspe1.n, 
        mspe1.reduced, 
        mspe1.f, 
        names = c("LASSO", 
                  "Ridge", 
                  # "Elastic Net", 
                  "Reduced", 
                  "Full"), 
        col = c("steelblue","gray80",
                # "pink", 
                "tomato", "springgreen"), 
        cex.axis = 1, 
        cex.lab = 1, 
        cex.main = 2,
        main = "Goodness of Fit",
        ylab = "MSE")

boxplot(mspe.la, 
        mspe.ri,
        # mspe.el, 
        # mspe.n, 
        mspe.reduced, 
        mspe.f, 
        names = c("LASSO", "Ridge", 
                  # "Elastic Net", 
                  "Reduced", "Full"), 
        col = c("steelblue","gray80",
                # "pink", 
                "tomato", "springgreen"), 
        cex.axis = 1, 
        cex.lab = 1, 
        cex.main = 2,
        main = "Prediction Power",
        ylab = "MSPE")

mtext(expression(hat(MSPE)), side = 2, line = 2.5)

>>>>

boxplot(mspe1.la, 
        mspe1.ri,
        # mspe1.el, 
        # mspe1.n, 
        mspe1.reduced, 
        mspe1.f, 
        names = c("LASSO", 
                  "Ridge", 
                  # "Elastic Net", 
                  "Reduced", 
                  "Full"), 
        col = c("steelblue","gray80",
                # "pink", 
                "tomato", "springgreen"), 
        cex.axis = 1, 
        cex.lab = 1, 
        cex.main = 2,
        main = "Goodness of Fit",
        ylab = expression(hat(MSE)))

boxplot(mspe.la, 
        mspe.ri,
        # mspe.el, 
        # mspe.n, 
        mspe.reduced, 
        mspe.f, 
        names = c("LASSO", "Ridge", 
                  # "Elastic Net", 
                  "Reduced", "Full"), 
        col = c("steelblue","gray80",
                # "pink", 
                "tomato", "springgreen"), 
        cex.axis = 1, 
        cex.lab = 1, 
        cex.main = 2,
        main = "Prediction Power",
        ylab = expression(hat(MSPE)))
